---
title: "Supporting nice tables for Q reviews"
author: adapted from"jdavis"
date: "1/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


We'll be reproducing the table located here:
https://docs.google.com/presentation/d/1tR3a81fd5mtkAX-RkX3hZv7skahkHryIrbrI7mli1Pc/edit#slide=id.p6


T
## Libraries + globals
  
```{r}
library(tidyverse)
library(glamr)
#install.packages("gt")
library(gt)
library(googledrive)
library(googlesheets4)
library(ICPIutilities)
library(glitr)
library(RColorBrewer)
library(scales)
library(dplyr)
library(extrafont)
library(scales)
library(tidytext)
library(patchwork)
library(ggtext)
library(glue)
library(janitor)
library(lubridate)
library(readxl)
library(readexcel)


pal <- RColorBrewer::brewer.pal(5, "Spectral")[2:5] ## we'll come back to this

```
  
##munging your data
  We're going to look at a simple table that's in long format and convert to wide using `pivot_wider
  
```{r}
## load raw OU x IM file
 raw <- read_msd("Data/MER_Structured_Datasets_OU_IM_FY19-21_20210514_v1_1.txt")
df<-as.data.frame(raw)
# # 
  df<-df%>% dplyr::filter(operatingunit == "Democratic Republic of the Congo",
          standardizeddisaggregate == "Total Numerator",
  
                    indicator %in% c("HTS_TST", "HTS_TST_POS", "TX_NEW", "TX_CURR", "TX_NET_NEW", "VMMC_CIRC", "PrEP_NEW","SC_CURR", "PMTCT_EID"),
          fiscal_year %in% c(2021))%>% 
   reshape_msd("long") 
   
# # group by period types and quarters
 df<-df%>%
   mutate(period_types = glue("{`period`} {`period_type`}"))
   
  df <- df %>% 
   dplyr::group_by(fundingagency,indicator, period_types) %>% 
   dplyr::summarise(value = sum(value))
 
 

#filter to usaid and pivot longer
  df <- df %>%
  #filter(fundingagency == "USAID") %>% 
  tidyr::pivot_wider(names_from = period_types,
              values_from = value)
 df<-df%>%
   mutate(`FY21 Achieved` =  `FY21 cumulative`/`FY21 targets`)%>%
   rename(`FY21 Q1`=`FY21Q1 results`,
          `FY21 Q2`=`FY21Q2 results`)
 
  raw <- read_msd("Data/MER_Structured_Datasets_PSNU_IM_FY19-21_20210514_v1_1_Democratic Republic of the Congo.txt")
df<-as.data.frame(raw)
# # 
  df<-df%>% dplyr::filter(operatingunit == "Democratic Republic of the Congo",
          standardizeddisaggregate == "Total Numerator",
  
                    indicator %in% c("HTS_TST", "HTS_TST_POS", "TX_NEW", "TX_CURR", "TX_NET_NEW", "VMMC_CIRC", "PrEP_NEW","SC_CURR", "PMTCT_EID","TX_PVLS"),
          fiscal_year %in% c(2021))%>% 
   reshape_msd("long") 
   
# # group by period types and quarters
 df<-df%>%
   mutate(period_types = glue("{`period`} {`period_type`}"))
   
  df <- df %>% 
   dplyr::group_by(snu1,indicator, period_types) %>% 
   dplyr::summarise(value = sum(value))
  df<-df%>%
    dplyr::filter(snu1 != "_Military Democratic Republic of the Congo")
 
 

#filter to usaid and pivot longer
  df <- df %>%
  filter(fundingagency == "USAID") %>% 
  tidyr::pivot_wider(names_from = period_types,
              values_from = value)
 df<-df%>%
   mutate(`FY21 Achieved` =  `FY21 cumulative`/`FY21 targets`)%>%
   rename(`FY21 Q1`=`FY21Q1 results`,
          `FY21 Q2`=`FY21Q2 results`)



```

```{r}

df %>% 
  gt()

## you can see that without doing any modification whatsoever, `gt` spits out a pretty good table with just the defaults
## but we want to clean this up a bit




df <- df %>%
    dplyr::relocate(`FY21 cumulative`, .before = `FY21 targets`) %>% 
    dplyr::relocate(`FY21 targets`, .before = `FY21 Achieved`) %>%
    dplyr::relocate(`FY21 Q2`, .before=`FY21 cumulative`)%>%
    dplyr::relocate(`FY21 Q1`, .before=`FY21 Q2`)%>%
    mutate(indicator = fct_relevel(indicator, "HTS_TST",
                                   "HTS_TST_POS",
                                   "TX_NEW",
                                   "TX_CURR",
                                   "TX_NET_NEW",
                                   "VMMC_CIRC",
                                   "PrEP_NEW","SC_CURR", "PMTCT_EID","TX_PVLS")) %>% 
    arrange(indicator)
```

 


```{r}
#add in decimals, and commas, and get rid of NAs
tbl1<-df %>% 
  gt(groupname_col = "fundingagency",
    rowname_col = "indicator") %>% 
  fmt_number(
    columns = vars(
      `FY21 Q1`,
      `FY21 Q2`,
      `FY21 cumulative`,
      `FY21 targets`),
    decimals = 0
  ) %>% 
  fmt_percent(
    columns = vars(`FY21 Achieved`),
    decimals = 0
  )%>%
  fmt_missing(columns = everything(),
            missing_text = "-")%>%
   tab_options(
    table.font.names = "Source Sans Pro"
    ) %>% 
   cols_width(
    vars(indicator) ~ px(140),
    everything() ~ px(80)
  )%>%
 
  tab_style(
    style = cell_borders(
      sides = "right",
      weight = px(1.5),
    ),
    locations = cells_body(
      columns = everything(),
      rows = everything()
    ))%>%
   tab_spanner(
    label = "FY21 Results",
    columns = c( "FY21 Q1",
      "FY21 Q2",
      "FY21 cumulative"))%>%


  tab_style(style = cell_fill(color = pal[4]),      ## defining the what (the 4th value of the pal object)
              locations = cells_body(                 ## telling it where (ie, the body of a cell)
                columns = vars(`FY21 Achieved`),      ## which col this refers to (note `vars()`)
                rows = `FY21 Achieved` >= 1.1)) %>%   ## the argument
    tab_style(style = cell_fill(color = pal[3]),
              locations = cells_body(
                columns = vars(`FY21 Achieved`),
                rows = `FY21 Achieved` < 1.1)) %>% 
    tab_style(style = cell_fill(color = pal[2]),
              locations = cells_body(
                columns = vars(`FY21 Achieved`),
                rows = `FY21 Achieved` < .9)) %>% 
    tab_style(style = cell_fill(color = pal[1]),
              locations = cells_body(
                columns = vars(`FY21 Achieved`),
                rows = `FY21 Achieved` < .75))%>%
 tab_header(title = "PEPFAR/DRC results, performance, and targets FY21 Q1-Q2") %>% 
  tab_source_note("Source: MSD FY20Q2i 2021-05-20")

tbl1%>%gtsave("partner performance.png")
  


# a few things to note: become familiar with the defaults for some of these (see help) for ex, we didn't include 
# `use_seps = TRUE` after line 136. This is true by default and defaults to a "," separator, but you can change this

```
Do the same as above but for just USAID partners
```{R}
df4<-as.data.frame(raw)
# # 
  df4<-df4%>% dplyr::filter(operatingunit == "Democratic Republic of the Congo",
          standardizeddisaggregate == "Total Numerator",
  
                    indicator %in% c("HTS_TST", "HTS_TST_POS", "TX_NEW", "TX_CURR", "TX_NET_NEW", "VMMC_CIRC", "PrEP_NEW","SC_CURR", "PMTCT_EID","TX_PVLS","HTS_INDEX"),
          fiscal_year %in% c(2021))%>% 
   reshape_msd("long") 
   
# # group by period types and quarters
 df4<-df4%>%
   mutate(period_types = glue("{`period`} {`period_type`}"))
   
  df4<- df4 %>% 
   dplyr::group_by(fundingagency,primepartner,indicator, period_types) %>% 
   dplyr::summarise(value = sum(value))
 
 
 

#filter to usaid and pivot longer
  df4 <- df4 %>%
  filter(fundingagency == "USAID") %>% 
   #filter(indicator %in% c("HTS_TST","HTS_TST_POS", "PMTCT_EID"))%>%
  tidyr::pivot_wider(names_from = period_types,
              values_from = value)
 df4<-df4%>%
   mutate(`FY21 Achieved` =  `FY21 cumulative`/`FY21 targets`)%>%
   rename(`FY21 Q1`=`FY21Q1 results`,
          `FY21 Q2`=`FY21Q2 results`,
          `Prime Partner`=`primepartner`)
df4 <- df4 %>%
    dplyr::relocate(`FY21 cumulative`, .before = `FY21 targets`) %>% 
    dplyr::relocate(`FY21 targets`, .before = `FY21 Achieved`) %>%
    dplyr::relocate(`FY21 Q2`, .before=`FY21 cumulative`)%>%
    dplyr::relocate(`FY21 Q1`, .before=`FY21 Q2`)%>%
    mutate(indicator = fct_relevel(indicator, "HTS_TST",
                                   "HTS_TST_POS",
                                   "TX_NEW",
                                   "TX_CURR",
                                   "TX_NET_NEW",
                                   "VMMC_CIRC",
                                   "PrEP_NEW","SC_CURR", "PMTCT_EID","TX_PVLS","HTS_INDEX")) %>% 
    arrange(indicator)

df_tst<-df4%>%
   filter(`indicator` %in% c("HTS_INDEX","HTS_TST","HTS_TST_POS", "PMTCT_EID"))
df_tx<-df4%>%
  filter(`indicator` %in% c("TX_CURR","TX_NEW"))


tbl5<-df_tst %>% 
  #group_by(`indicator`, `Prime Partner`)%>%
  #filter(`indicator` == "HTS_TST","HTS_TST_POS", "PMTCT_EID")%>%
  gt(groupname_col = "indicator",
    rowname_col = "Prime Partner")%>% 
   cols_hide(
    columns = c("fundingagency","indicator","Prime Partner"))%>% #hide agency
  fmt_number(
    columns = vars(
      `FY21 Q1`,
      `FY21 Q2`,
      `FY21 cumulative`,
      `FY21 targets`),
    decimals = 0
  ) %>% 
  fmt_percent(
    columns = vars(`FY21 Achieved`),
    decimals = 0
  )%>%
  fmt_missing(columns = everything(),
            missing_text = "-")%>%
   tab_options(
    table.font.names = "Source Sans Pro"
    ) %>% 
   cols_width(
    vars("Prime Partner") ~ px(140),
    everything() ~ px(80)
  )%>%
  tab_style(
    style = cell_borders(
      sides = "right",
      weight = px(1.5),
    ),
    locations = cells_body(
      columns = everything(),
      rows = everything()
    ))%>%
  
   tab_spanner(
    label = "COP20 Results",
    columns = c( "FY21 Q1",
      "FY21 Q2",
      "FY21 cumulative"))%>%tab_style(style = cell_fill(color = pal[4]),      ## defining the what (the 4th value of the pal object)
              locations = cells_body(                 ## telling it where (ie, the body of a cell)
                columns = vars(`FY21 Achieved`),      ## which col this refers to (note `vars()`)
                rows = `FY21 Achieved` >= 1.1)) %>%   ## the argument
    tab_style(style = cell_fill(color = pal[3]),
              locations = cells_body(
                columns = vars(`FY21 Achieved`),
                rows = `FY21 Achieved` < 1.1)) %>% 
    tab_style(style = cell_fill(color = pal[2]),
              locations = cells_body(
                columns = vars(`FY21 Achieved`),
                rows = `FY21 Achieved` < .9)) %>% 
    tab_style(style = cell_fill(color = pal[1]),
              locations = cells_body(
                columns = vars(`FY21 Achieved`),
                rows = `FY21 Achieved` < .75))%>%
 tab_header(title = "USAID Testing Results, Performance, and Targets FY21 Q1-Q2") %>% 
  tab_source_note("Source: MSD FY20Q2i 2021-05-20")
tbl5%>%gtsave("tst usaid performance.png")

      tab_style(style = list(cell_fill(color = old_rose_light, alpha = 0.75)),
            locations = cells_body(
              columns = c("FY21 Achieved"),
              rows = "FY21 Achieved" < 0.25 & "indicator" != "TX_CURR")
  ) %>% 
    tab_style(style = list(cell_fill(color = burnt_sienna_light, alpha = 0.75)),
              locations = cells_body(
                columns = c("FY21 Achieved"),
                rows = "FY21 Achieved" >= 0.25 & "FY21 Achieved" < 0.4 & "indicator" != "TX_CURR")
    ) %>% 
    tab_style(style = list(cell_fill(color = scooter_light, alpha = 0.75)),
              locations = cells_body(
                columns = c("FY21 Achieved"),
                rows = "FY21 Achieved" >= 0.4 & "FY21 Achieved" < 0.6 & "indicator" != "TX_CURR")
    ) %>% 
    tab_style(style = list(cell_fill(color = trolley_grey_light, alpha = 0.75)),
              locations = cells_body(
                columns = c("FY21 Achieved"),
                rows = "FY21 Achieved" >= 0.6 & "indicator" != "TX_CURR")
              ) %>% 
    
  # NOW TX_CURR
  tab_style(style = list(cell_fill(color = old_rose_light, alpha = 0.75)),
            locations = cells_body(
              columns = c("FY21 Achieved"),
              rows = "FY21 Achieved" < 0.75 & "indicator" == "TX_CURR")
  ) %>% 
    tab_style(style = list(cell_fill(color = burnt_sienna_light, alpha = 0.75)),
              locations = cells_body(
                columns = c("FY21 Achieved"),
                rows = "FY21 Achieved" >= 0.75 & "FY21 Achieved" < 0.9 & "indicator" == "TX_CURR")
    ) %>% 
    tab_style(style = list(cell_fill(color = scooter_light, alpha = 0.75)),
              locations = cells_body(
                columns = c("FY21 Achieved"),
                rows = "FY21 Achieved" >= 0.9 & "FY21 Achieved" < 1.1 & "indicator" == "TX_CURR")
    ) %>% 
    tab_style(style = list(cell_fill(color = trolley_grey_light, alpha = 0.75)),
              locations = cells_body(
                columns = c("FY21 Achieved"),
                rows = "FY21 Achieved" >= 1.1 & "indicator" == "TX_CURR")
    )%>%
 tab_header(title = "USAID Partners results, performance, and targets FY21 Q1-Q2") %>% 
  tab_source_note("Source: MSD FY20Q2i 2021-05-20")
```

#SNU
```{r}
   dfhk<-df%>%
    dplyr::filter(snu1 == "Haut Katanga")
    dfk<-df%>%
    dplyr::filter(snu1 == "Kinshasa")
     dfl<-df%>%
    dplyr::filter(snu1 == "Lualaba")
tblhk<-dfhk %>% 
  gt(groupname_col = "snu1",
    rowname_col = "indicator") %>% 
  fmt_number(
    columns = vars(
      `FY21 Q1`,
      `FY21 Q2`,
      `FY21 cumulative`,
      `FY21 targets`),
    decimals = 0
  ) %>% 
  fmt_percent(
    columns = vars(`FY21 Achieved`),
    decimals = 0
  )%>%
  fmt_missing(columns = everything(),
            missing_text = "-")%>%
   tab_options(
    table.font.names = "Source Sans Pro"
    ) %>% 
   cols_width(
    vars(indicator) ~ px(140),
    everything() ~ px(80)
  )%>%
 
  tab_style(
    style = cell_borders(
      sides = "right",
      weight = px(1.5),
    ),
    locations = cells_body(
      columns = everything(),
      rows = everything()
    ))%>%
   tab_spanner(
    label = "FY21 Results",
    columns = c( "FY21 Q1",
      "FY21 Q2",
      "FY21 cumulative"))%>%


  tab_style(style = cell_fill(color = pal[4]),      ## defining the what (the 4th value of the pal object)
              locations = cells_body(                 ## telling it where (ie, the body of a cell)
                columns = vars(`FY21 Achieved`),      ## which col this refers to (note `vars()`)
                rows = `FY21 Achieved` >= 1.1)) %>%   ## the argument
    tab_style(style = cell_fill(color = pal[3]),
              locations = cells_body(
                columns = vars(`FY21 Achieved`),
                rows = `FY21 Achieved` < 1.1)) %>% 
    tab_style(style = cell_fill(color = pal[2]),
              locations = cells_body(
                columns = vars(`FY21 Achieved`),
                rows = `FY21 Achieved` < .9)) %>% 
    tab_style(style = cell_fill(color = pal[1]),
              locations = cells_body(
                columns = vars(`FY21 Achieved`),
                rows = `FY21 Achieved` < .75))%>%
 tab_header(title = "PEPFAR/DRC results, performance, and targets FY21 Q1-Q2") %>% 
  tab_source_note("Source: MSD FY20Q2i 2021-05-20")

  
  
  tbll<-dfl %>% 
  gt(groupname_col = "snu1",
    rowname_col = "indicator") %>% 
  fmt_number(
    columns = vars(
      `FY21 Q1`,
      `FY21 Q2`,
      `FY21 cumulative`,
      `FY21 targets`),
    decimals = 0
  ) %>% 
  fmt_percent(
    columns = vars(`FY21 Achieved`),
    decimals = 0
  )%>%
  fmt_missing(columns = everything(),
            missing_text = "-")%>%
   tab_options(
    table.font.names = "Source Sans Pro"
    ) %>% 
   cols_width(
    vars(indicator) ~ px(140),
    everything() ~ px(80)
  )%>%
 
  tab_style(
    style = cell_borders(
      sides = "right",
      weight = px(1.5),
    ),
    locations = cells_body(
      columns = everything(),
      rows = everything()
    ))%>%
   tab_spanner(
    label = "FY21 Results",
    columns = c( "FY21 Q1",
      "FY21 Q2",
      "FY21 cumulative"))%>%


  tab_style(style = cell_fill(color = pal[4]),      ## defining the what (the 4th value of the pal object)
              locations = cells_body(                 ## telling it where (ie, the body of a cell)
                columns = vars(`FY21 Achieved`),      ## which col this refers to (note `vars()`)
                rows = `FY21 Achieved` >= 1.1)) %>%   ## the argument
    tab_style(style = cell_fill(color = pal[3]),
              locations = cells_body(
                columns = vars(`FY21 Achieved`),
                rows = `FY21 Achieved` < 1.1)) %>% 
    tab_style(style = cell_fill(color = pal[2]),
              locations = cells_body(
                columns = vars(`FY21 Achieved`),
                rows = `FY21 Achieved` < .9)) %>% 
    tab_style(style = cell_fill(color = pal[1]),
              locations = cells_body(
                columns = vars(`FY21 Achieved`),
                rows = `FY21 Achieved` < .75))%>%
 tab_header(title = "PEPFAR/DRC results, performance, and targets FY21 Q1-Q2") %>% 
  tab_source_note("Source: MSD FY20Q2i 2021-05-20")
  
  
tblk<-  dfk %>% 
  gt(groupname_col = "snu1",
    rowname_col = "indicator") %>% 
  fmt_number(
    columns = vars(
      `FY21 Q1`,
      `FY21 Q2`,
      `FY21 cumulative`,
      `FY21 targets`),
    decimals = 0
  ) %>% 
  fmt_percent(
    columns = vars(`FY21 Achieved`),
    decimals = 0
  )%>%
  fmt_missing(columns = everything(),
            missing_text = "-")%>%
   tab_options(
    table.font.names = "Source Sans Pro"
    ) %>% 
   cols_width(
    vars(indicator) ~ px(140),
    everything() ~ px(80)
  )%>%
 
  tab_style(
    style = cell_borders(
      sides = "right",
      weight = px(1.5),
    ),
    locations = cells_body(
      columns = everything(),
      rows = everything()
    ))%>%
   tab_spanner(
    label = "FY21 Results",
    columns = c( "FY21 Q1",
      "FY21 Q2",
      "FY21 cumulative"))%>%


  tab_style(style = cell_fill(color = pal[4]),      ## defining the what (the 4th value of the pal object)
              locations = cells_body(                 ## telling it where (ie, the body of a cell)
                columns = vars(`FY21 Achieved`),      ## which col this refers to (note `vars()`)
                rows = `FY21 Achieved` >= 1.1)) %>%   ## the argument
    tab_style(style = cell_fill(color = pal[3]),
              locations = cells_body(
                columns = vars(`FY21 Achieved`),
                rows = `FY21 Achieved` < 1.1)) %>% 
    tab_style(style = cell_fill(color = pal[2]),
              locations = cells_body(
                columns = vars(`FY21 Achieved`),
                rows = `FY21 Achieved` < .9)) %>% 
    tab_style(style = cell_fill(color = pal[1]),
              locations = cells_body(
                columns = vars(`FY21 Achieved`),
                rows = `FY21 Achieved` < .75))%>%
 tab_header(title = "PEPFAR/DRC results, performance, and targets FY21 Q1-Q2") %>% 
  tab_source_note("Source: MSD FY20Q2i 2021-05-20")
  
  


tblhk%>%gtsave("hk performance.png")
tblk%>%gtsave("k performance.png")
tbll%>%gtsave("l performance.png")

```

```{r}
tbltx<-df_tx %>% 
  #group_by(`indicator`, `Prime Partner`)%>%
  #filter(`indicator` == "HTS_TST","HTS_TST_POS", "PMTCT_EID")%>%
  gt(groupname_col = "indicator",
    rowname_col = "Prime Partner")%>% 
   cols_hide(
    columns = c("fundingagency","indicator","Prime Partner"))%>% #hide agency
  fmt_number(
    columns = vars(
      `FY21 Q1`,
      `FY21 Q2`,
      `FY21 cumulative`,
      `FY21 targets`),
    decimals = 0
  ) %>% 
  fmt_percent(
    columns = vars(`FY21 Achieved`),
    decimals = 0
  )%>%
  fmt_missing(columns = everything(),
            missing_text = "-")%>%
   tab_options(
    table.font.names = "Source Sans Pro"
    ) %>% 
   cols_width(
    vars("Prime Partner") ~ px(140),
    everything() ~ px(80)
  )%>%
  tab_style(
    style = cell_borders(
      sides = "right",
      weight = px(1.5),
    ),
    locations = cells_body(
      columns = everything(),
      rows = everything()
    ))%>%
  
   tab_spanner(
    label = "COP20 Results",
    columns = c( "FY21 Q1",
      "FY21 Q2",
      "FY21 cumulative"))%>%tab_style(style = cell_fill(color = pal[4]),      ## defining the what (the 4th value of the pal object)
              locations = cells_body(                 ## telling it where (ie, the body of a cell)
                columns = vars(`FY21 Achieved`),      ## which col this refers to (note `vars()`)
                rows = `FY21 Achieved` >= 1.1)) %>%   ## the argument
    tab_style(style = cell_fill(color = pal[3]),
              locations = cells_body(
                columns = vars(`FY21 Achieved`),
                rows = `FY21 Achieved` < 1.1)) %>% 
    tab_style(style = cell_fill(color = pal[2]),
              locations = cells_body(
                columns = vars(`FY21 Achieved`),
                rows = `FY21 Achieved` < .9)) %>% 
    tab_style(style = cell_fill(color = pal[1]),
              locations = cells_body(
                columns = vars(`FY21 Achieved`),
                rows = `FY21 Achieved` < .75))%>%
 tab_header(title = "USAID Treatment Results, Performance, and Targets FY21 Q1-Q2") %>% 
  tab_source_note("Source: MSD FY20Q2i 2021-05-20")
tbltx%>%gtsave("tx usaid performance.png")



DRC_VLC_VLS <- read_excel("Data/DRC VLC_VLS.xlsx")
     
df_VLC<-DRC_VLC_VLS
tblvc<-df_VLC%>%

  #group_by(`indicator`, `Prime Partner`)%>%
  #filter(`indicator` == "HTS_TST","HTS_TST_POS", "PMTCT_EID")%>%
  gt(groupname_col = "Indicator",
    rowname_col = "Prime Partner")%>% 
  # cols_hide(
   # columns = c("fundingagency","indicator","Prime Partner"))%>% #hide agency
  fmt_number(
    columns = vars(
      `FY21 Q1`,
      `FY21 Q2`,
      `FY21 cumulative`,
      `FY21 targets`),
    decimals = 0
  ) %>% 
  fmt_percent(
    columns = vars(`FY21 Achieved`),
    decimals = 0
  )%>%
  fmt_missing(columns = everything(),
            missing_text = "-")%>%
   tab_options(
    table.font.names = "Source Sans Pro"
    ) %>% 
   cols_width(
    vars("Prime Partner") ~ px(140),
    everything() ~ px(80)
  )%>%
  tab_style(
    style = cell_borders(
      sides = "right",
      weight = px(1.5),
    ),
    locations = cells_body(
      columns = everything(),
      rows = everything()
    ))%>%
  
   tab_spanner(
    label = "COP20 Results",
    columns = c( "FY21 Q1",
      "FY21 Q2",
      "FY21 cumulative"))%>%tab_style(style = cell_fill(color = pal[4]),      ## defining the what (the 4th value of the pal object)
              locations = cells_body(                 ## telling it where (ie, the body of a cell)
                columns = vars(`FY21 Achieved`),      ## which col this refers to (note `vars()`)
                rows = `FY21 Achieved` >= 1.1)) %>%   ## the argument
    tab_style(style = cell_fill(color = pal[3]),
              locations = cells_body(
                columns = vars(`FY21 Achieved`),
                rows = `FY21 Achieved` < 1.1)) %>% 
    tab_style(style = cell_fill(color = pal[2]),
              locations = cells_body(
                columns = vars(`FY21 Achieved`),
                rows = `FY21 Achieved` < .9)) %>% 
    tab_style(style = cell_fill(color = pal[1]),
              locations = cells_body(
                columns = vars(`FY21 Achieved`),
                rows = `FY21 Achieved` < .75))%>%
 tab_header(title = "USAID Viral Suppression FY21 Q1-Q2") %>% 
  tab_source_note("Source: MSD FY20Q2i 2021-05-20")
tblvc%>%gtsave("vls usaid performance.png")